### 2017-03-25 paper/topologySkeletons.tex
wip on the paper

\begin{lstlisting}[frame=htrbl]
pipe :: (ArrowLoop arr,
	ArrowParallel arr (fut a) (fut a) conf, Future fut a) =>
	conf -> [arr a a] -> arr a a
pipe conf fs = unliftFut (pipeFut conf fs)

pipeFut :: (ArrowLoop arr,
	ArrowParallel arr (fut a) (fut a) conf, Future fut a) =>
	conf -> [arr a a] -> arr (fut a) (fut a)
pipeFut conf fs =
	loop (arr snd &&& (arr (uncurry (:) >>> lazy) >>>
		parEvalNFut conf fs)) >>>
	arr last
\end{lstlisting}

>>>>

The parallel pipe skeleton is semantically equivalent to folding over a list \code{[arr a a]} of arrows with \code{>>>}, but does this in parallel, meaning that the arrows don't have to reside on the same thread/machine. We implement this skeleton using the \code{ArrowLoop} typeclass which enables us to use \code{loop :: arr (a, b) (c, b) -> arr a c}.

\begin{lstlisting}[frame=htrbl]
pipeSimple :: (ArrowLoop arr, ArrowParallel arr a a conf) =>
	conf -> [arr a a] -> arr a a
pipeSimple conf fs =
	loop (arr snd &&& (arr (uncurry (:) >>> lazy) >>>
		parEvalN conf fs)) >>>
	arr last
\end{lstlisting}
where \code{lazy} is defined as:
\begin{lstlisting}[frame=htrbl]
lazy :: (Arrow arr) => arr [a] [a]
lazy = arr (\ ~(x:xs) -> x : lazy xs)
\end{lstlisting}
However, using this definition directly, will result in the master node becoming a potential bottleneck in distributed environments as described in chapter \ref{futures}. Therefore, a more sophisticated version that uses Futures internally is a good idea:
\begin{lstlisting}[frame=htrbl]
pipe :: (ArrowLoop arr, ArrowParallel arr (fut a) (fut a) conf,
	Future fut a) =>
	conf -> [arr a a] -> arr a a
pipe conf fs = unliftFut (pipeSimple conf (map liftFut fs))
\end{lstlisting}
Sometimes, this pipe definition can be a bit inconvenient, especially if we want to pipe arrows of different types to each other.
\begin{lstlisting}[frame=htrbl]
pipe2 :: (ArrowLoop arr, ArrowChoice arr,
	ArrowParallel arr (fut (([a], [b]), [c])) (fut (([a], [b]), [c])) conf,
	Future fut (([a], [b]), [c])) =>
	conf -> arr a b -> arr b c -> arr a c
pipe2 conf f g = 
	arr (\a -> (([a], []), [])) >>>
	pipe conf (replicate 2 $ unify f g) >>>
	arr snd >>>
	arr head
		where
			unify :: (ArrowChoice arr) =>
				arr a b -> arr b c -> arr (([a], [b]), [c]) (([a], [b]), [c])
			unify f g =
				(mapArr f *** mapArr g) *** arr (\_ -> []) >>>
				arr (\((a, b), c) -> ((c, a), b))
\end{lstlisting}
Note that extensive use of this combinator over \code{pipe} with a hand-written combination data-type will probably result in worse performance because of more communication overhead from the many calls to parEvalN. Nonetheless, we can define a parallel piping operator \code{|>>>|} which is semantically equivalent to \code{>>>} similar to the other parallel syntactic sugar from chapter \ref{syntacticSugar}:
\begin{lstlisting}[frame=htrbl]
(|>>>|) :: (ArrowLoop arr, ArrowChoice arr,
	ArrowParallel arr (fut (([a], [b]), [c])) (fut (([a], [b]), [c])) (),
	Future fut (([a], [b]), [c])) =>
	arr a b -> arr b c -> arr a c
(|>>>|) = pipe2 ()
\end{lstlisting}
